\documentclass[11pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[british]{babel}
\usepackage{newtxtext,newtxmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{array}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{amsmath}
\usepackage{float}
\usepackage{caption}
\usepackage{setspace}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=black, citecolor=black, urlcolor=black}

\begin{document}

\appendix

\section{Runaway / Verbosity Handling}
\label{app:verbosity}

A subset of C4-Den-Mat outputs contained repeated \texttt{TRANSCRIPT} blocks or
very long outputs with WER $>$ 1.0 (one dialogue reached WER 10.25). These are
treated as prompt-following failures rather than meaningful corrections.

Any output that (a) contained more than one literal \texttt{TRANSCRIPT}
marker, or (b) exceeded five times the reference word count, was flagged as a
runaway. Flagged runs were manually checked and recorded in the file
\texttt{c4\_den\_mat\_cleaned.json}. Metrics can therefore be reported in two
ways:
\begin{itemize}[leftmargin=1.4em]
  \item \textbf{Full}: all runs included (no exclusions).
  \item \textbf{Cleaned}: flagged runaways removed using the above rule.
\end{itemize}
Tables in the main paper use \textbf{Full} metrics unless explicitly marked as
``Cleaned''. Appendix~\ref{app:cleaned-metrics} lists the affected dialogue
IDs and summarises both versions side by side so that the impact of removing
runaways is transparent.

\section{Reproducibility Checklist}
\label{app:repro}

The following settings were used in all main experiments.

\subsection*{ASR}
\begin{itemize}[leftmargin=1.4em]
  \item Whisper model: \texttt{openai/whisper-tiny}.
  \item Decoding: beam size = 5, temperature = 0.0, no timestamps, language = en.
  \item Audio sampling rate: dataset-provided sampling rate (as released with
        each corpus; no resampling performed beyond the dataset defaults).
\end{itemize}

\subsection*{Retrieval Embeddings and FAISS}
\begin{itemize}[leftmargin=1.4em]
  \item Embedding model: \texttt{sentence-transformers/all-MiniLM-L6-v2}.
  \item Embeddings L2-normalised before indexing.
  \item FAISS index: \texttt{IndexFlatIP} (inner product), top-$k = 3$ passages per query.
\end{itemize}

\subsection*{BM25 Lexical Retrieval}
\begin{itemize}[leftmargin=1.4em]
  \item Library: \texttt{rank\_bm25}.
  \item Parameters: $k_1 = 1.2$, $b = 0.75$.
  \item Tokenisation: whitespace tokeniser with lowercasing and punctuation stripping.
\end{itemize}

\subsection*{Chunking}
\begin{itemize}[leftmargin=1.4em]
  \item Transcript chunks: 400 words with 50-word overlap (whitespace tokenisation).
  \item PriMock57 passages (for cross-dataset retrieval): 180-word chunks with 30-word overlap.
\end{itemize}

\subsection*{LLMs and Generation}
\begin{itemize}[leftmargin=1.4em]
  \item Primary model: Mistral-7B via Ollama image \texttt{mistral:latest}.
  \item Supplementary baseline: LLaMA-3 8B via Ollama (default LLaMA-3 8B image).
  \item Mistral decoding: temperature = 0.0, top\_p = 0.95, max\_new\_tokens = 256,
        repetition\_penalty = 1.0, stop sequence = \verb|\n\n|.
  \item LLaMA-3 decoding: temperature = 0.0, top\_p = 0.90, max\_new\_tokens = 256,
        repetition\_penalty = 1.0, same stop sequence.
\end{itemize}

\subsection*{Prompts}
\begin{itemize}[leftmargin=1.4em]
  \item Base instruction (all conditions):
\begin{quote}\small
\texttt{Fix only clear ASR errors in this transcript excerpt. Output ONLY the corrected text. No commentary.}
\end{quote}
  \item RAG conditions prepend either \texttt{REFERENCE CONTEXT} (TED) or
        \texttt{BACKGROUND} (MTS / PriMock57) blocks as described in the main text.
  \item Full prompt templates for each condition (C2a, C2b, C3-*, C4-*) are listed
        in a separate prompt appendix or configuration file in the released code.
\end{itemize}

\subsection*{Randomness and Hardware}
\begin{itemize}[leftmargin=1.4em]
  \item Random seed: 42 for Python, NumPy, and any retrieval shuffles.
  \item Hardware: Fedora Linux laptop with NVIDIA GeForce RTX 5060 Laptop GPU
        (8\,GB VRAM) and an x86-64 CPU; evaluation scripts run on CPU.
\end{itemize}

\section{Annotated Examples (Template)}
\label{app:examples}

Table~\ref{tab:annotated-examples} illustrates the format used for qualitative
examples of successful and failed corrections. In the actual appendix, each
row should be filled with real examples drawn from MTS-Dialog and PriMock57.

\begin{table*}[!t]
\centering
\caption{Example layout for annotated corrections. Fill with real examples:
four successes and four failures.}
\label{tab:annotated-examples}
\small
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{\textwidth}{cXXXXXX}
\toprule
\textbf{ID} & \textbf{Gold} & \textbf{ASR} & \textbf{LLM-only} &
\textbf{BM25-RAG} & \textbf{Dense-RAG} & \textbf{Note} \\
\midrule
E1 & patient takes \textbf{metformin} &
     patient takes \textbf{metaprol} &
     patient takes metaprol &
     patient takes \textbf{metformin} &
     patient takes \textbf{metformin} &
     success -- RAG corrected a phonetic error. \\
E2 & patient has \textbf{asthma} &
     patient has \textbf{ask ma} &
     patient has asthma &
     patient has sarcoidosis &
     patient has sarcoidosis &
     failure -- dense RAG substituted a different diagnosis. \\
E3 & \multicolumn{6}{l}{\dots fill remaining rows with real successes / failures \dots} \\
\bottomrule
\end{tabularx}
\end{table*}

\section{Cleaned vs Full Metrics (Skeleton)}
\label{app:cleaned-metrics}

Table~\ref{tab:full-vs-cleaned} provides a skeleton for reporting metrics with
and without runaway outputs. Populate with real values for C4-Den-Mat on
MTS-Dialog once computed.

\begin{table}[H]
\centering
\caption{Skeleton for Full vs Cleaned metrics on MTS-Dialog C4-Den-Mat.
Replace placeholders with actual means, standard deviations, and sample sizes.}
\label{tab:full-vs-cleaned}
\small
\renewcommand{\arraystretch}{1.15}
\begin{tabular}{lcc}
\toprule
 & \textbf{Full} & \textbf{Cleaned} \\
\midrule
WER (mean $\pm$ SD)      & \textemdash{} & \textemdash{} \\
BLEU (mean $\pm$ SD)     & \textemdash{} & \textemdash{} \\
ROUGE-L (mean $\pm$ SD)  & \textemdash{} & \textemdash{} \\
BERTScore (mean $\pm$ SD)& \textemdash{} & \textemdash{} \\
DISEASE F1 (mean $\pm$ SD) & \textemdash{} & \textemdash{} \\
$n$ dialogues            & \textemdash{} & \textemdash{} \\
\bottomrule
\end{tabular}
\end{table}

\end{document}

